Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-01-26 src/sections/intro.tex
Started cleaning up introduction

\section{Introduction}\label{sec:Intro}
Whereas, people have have often tried to categorized objects as GCs by making
cuts along half-light radius, density, and surface brightness profile, in fact
many objects which are generally thought of as GCs don't cleanly fit into these
cuts. Consequently, \citet{Carretta2010} proposed a definition of GC based on
observed chemical inhomogeneities in their stellar populations. The modern
understanding of GCs then is not simply one of a dense cluster of stars which
may have chemical inhomogeneities and multiple populations; rather, it is one
where those chemical inhomogeneities and multiple populations themselves are
the defining element of a GC.

All globular clusters older than 2 Gyr studied in detail show populations
enriched in He, N, and Na while also being deplete in O and C
\citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
not strongly correlated with variations in heavy element abundances. One
consequence of this fact is the spectroscopically uniform Fe abundances
mentioned in \S\ref{sec:intro_GC}. Further, high-resolution spectral studies
reveal anti-correlations between N-C abundances, Na-O abundances, and
potentially Al-Mg \citep{Sneden1992, Gratton2012}. Typical stellar fusion
reactions can deplete core oxygen; however, the observed abundances of Na, Al,
and Mg cannot be explained by the likes of the CNO cycle \citep{Prantzos2007}.

Formation channels for these multiple populations remain a point of debate
among astronomers. Most proposed formation channels consist of some older,
more massive, population of stars polluting the pristine cluter media before a
second population forms, now enriched in heavier elements which they themselves could
not have generated \citep[for a detailed review see ][]{Gratton2012}. The four
primary candidates for these polluters are asymptotic giant branch stars
\citep[AGBs,][]{Ventura2001,DErcole2010}, fast rotating massive stars
\citep[FRMSs,][]{Decressin2007}, super massive stars
\citep[SMSs,][]{Denissenkov2014}, and massive interacing binaries
\citep[MIBs,][]{deMink2009, Bastian2018}.

>>>>

\section{Introduction}\label{sec:Intro}
Globular clusters (GCs) are among the oldest observ- able objects in the
universe \citep{Pen11}. They are characterized by high densities with typical
half-light radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses
ranging from $10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs
are signifigantly larger than these typical values {\color{red}EXAMPLE}. GCs
provide a unique way to probe stellar evolution \citep{Bau03}, galaxy formation
models \citep{Boy18,Kra05}, and dark matter halo struc- ture \citep{Hud18}.
{\color{red} BRING IN SOME MORE RECENT CITATIONS.}

Whereas, people have have often tried to categorized objects as GCs through
relations between half-light radius, density, and surface brightness profile,
in fact many objects which are generally thought of as GCs don't cleanly fit
into these cuts {\color{red} EXAMPLE + CITATION}. Consequently,
\citet{Carretta2010} proposed a definition of GC based on observed chemical
inhomogeneities in their stellar populations. The modern understanding of GCs
then is not simply one of a dense cluster of stars which may have chemical
inhomogeneities and multiple populations; rather, it is one where those
chemical inhomogeneities and multiple populations themselves are the defining
element of a GC.

All Milky Way globular clusters older than 2 Gyr studied in detail show
populations enriched in He, N, and Na while also being deplete in O and C
\citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
not strongly correlated with variations in heavy element abundance, resulting
in spectroscopically uniform Fe abundances between populations. Further,
high-resolution spectral studies reveal anti-correlations between N-C
abundances, Na-O abundances, and potentially Al-Mg \citep{Sneden1992,
Gratton2012}. Typical stellar fusion reactions can deplete core oxygen;
however, the observed abundances of Na, Al, and Mg cannot be explained by the
likes of the CNO cycle \citep{Prantzos2007}.

Formation channels for these multiple populations remain a point of debate
among astronomers. Most proposed formation channels consist of some older,
more massive, population of stars polluting the pristine cluster media before a
second population forms, now enriched in heavier elements which they themselves could
not have generated \citep[for a detailed review see ][]{Gratton2012}. The four
primary candidates for these polluters are asymptotic giant branch stars
\citep[AGBs,][]{Ventura2001,DErcole2010}, fast rotating massive stars
\citep[FRMSs,][]{Decressin2007}, super massive stars
\citep[SMSs,][]{Denissenkov2014}, and massive interacing binaries
\citep[MIBs,][]{deMink2009, Bastian2018}.
